Estimating Access to Rabies Post-Exposure Prophylaxis in Madagascar

### 2019-03-19 accessPEP.Rmd
some preliminary code for vial estimates

## Files
source("R/utils.R")
source("R/models.R")
source("R/data_functions.R")
source("R/get.burden.R")
select <- dplyr::select
knitr::opts_chunk$set(fig.pos = 'h', echo = FALSE, message = FALSE, warning = FALSE, 
                      results = "hide",
                      include = TRUE)
```

@@

dist_ttimes <- cbind(dist_catchments$ttimes_weighted, dist_ttimes)
dist_mat <- matrix(NA, nrow(dist_ttimes), ncol(dist_ttimes))
dist_mat[, 1] <- dist_ttimes[, 1]
for (i in 2:ncol(dist_ttimes)){
  dist_mat[, i] <- ifelse(dist_ttimes[, i] < dist_ttimes[, i - 1], dist_ttimes[, i], NA)
}
dist_mat <- as.data.table(dist_mat)
dist_mat$mdg_dis_co <- as.character(mada_district$mdg_dis_co)
dist_mat <- melt(dist_mat, id.vars = "mdg_dis_co", value.name = "ttimes", variable.name = "scenario")
dist_mat$scenario <- as.numeric(gsub("V", "", dist_mat$scenario)) - 1

@@

results_comm_med <- get.burden.stochastic(names = comm_mat$mdg_cm_, ttimes = comm_mat$ttimes/60,
                           pop = comm_mat$pop, scenario = comm_mat$scenario,
                           param_ttimes = B_ttimes_mada,
                           param_intercept = B_0_mada,
                           p_rab_min = 0.2, p_rab_max = 0.6, rho_max = 0.98,
                           max_HDR = 25, min_HDR = 5, 
                           dog_rabies_inc = 0.01, human_exp_rate = 0.39, 
                           prob_death = 0.16, nsims = 1000)

@@

results_dist_med <- get.burden.stochastic(names = dist_mat$mdg_dis_co, ttimes = dist_mat$ttimes/60,
                           pop = dist_mat$pop, scenario = dist_mat$scenario,
                           param_ttimes = B_ttimes_dist,
                           param_intercept = B_0_dist,
                           p_rab_min = 0.2, p_rab_max = 0.6, rho_max = 0.98,
                           max_HDR = 25, min_HDR = 5, 
                           dog_rabies_inc = 0.01, human_exp_rate = 0.39, 
                           prob_death = 0.16, nsims = 1000)

@@

``` {r scenario, cache = TRUE}
##
ctar_pts <- read.csv("output/incremental_ARMC_nofilter.csv")
ctar_pts$order <- 1:nrow(ctar_pts)
ggplot() + geom_polygon(data = gg_district, aes(x = long, y = lat, group = group), fill = "grey",
                         color = "grey50", alpha = 0.5) +
  geom_point(data = ctar_metadata, aes(x = LONGITUDE, y = LATITUDE), color = "black", shape = 1) +
  geom_point(data = ctar_pts, aes(x = Y_COORD, y = X_COORD, color = order, alpha = order))

## Plotting national level
ggplot(data = results_natl, aes (x = scenario, y = deaths_mean, color = model)) +
  geom_line() +
  geom_ribbon(aes(ymin = deaths_upperCI, ymax = deaths_lowerCI, 
                  color = NULL, fill = model),
              alpha = 0.5) +
  scale_color_manual(values = c("district" = "blue", 
                                "commune" = "purple"), 
                     guide = "none") +
  scale_fill_manual(values = c("district" = "blue", 
                                "commune" = "purple")) +
  guides(color = guide_legend(), 
         fill = guide_legend(override.aes = list(linetype = 1))) +
  xlab("# of Additional ARMC") +
  ylab("Mean annual deaths \n due to rabies") +
  labs(tag = "A") -> e

@@

ggplot(data = results_all, aes(x = averted_mean, y = reorder(district, ttimes_weighted), 
                               color = scenario)) +
  ggstance::geom_pointrangeh(aes(xmin = deaths_lowerCI, xmax = deaths_upperCI), alpha = 0.25,
                             fatten = 2) +
  facet_wrap(~model)

@@

We use this to estimate how vaccine demand will change as access to PEP is expanded...

@@

### S5. Sensitity analyses for burden estimates

#### District
```{r scaling w/ pop, cache = TRUE}
## Dist ttimes
dist_ttimes <- read.csv("output/district_temp_scenario_20190212_181056.csv", row.names = 1)
dist_ttimes <- as.data.table(dist_ttimes)
dist_ttimes$mdg_dis_co <- as.character(mada_district$mdg_dis_co)
dist_ttimes <- melt(dist_ttimes, id.vars = "mdg_dis_co", value.name = "ttimes", variable.name = "scenario")
dist_ttimes$scenario <- as.numeric(gsub("result.", "", dist_ttimes$scenario))
dist_ttimes <- rbind(dist_ttimes, 
                       as.data.frame(list(mdg_dis_co = dist_catchments$mdg_dis_co, scenario = 0,
                                          ttimes = dist_catchments$ttimes_weighted)))
dist_ttimes %>%
  left_join(select(mada_district@data, mdg_dis_co, district, pop = pop2015adj)) -> dist_ttimes

@@

scale_df_dist %>%
  merge(., select(mada_district@data, mdg_dis_co, ttimes_weighted, pop = pop2015adj)) -> scale_df_check
ggplot(data = scale_df_check, aes(x = log(pop), 
                            y = constrained_inc(sf, intercept, pop, inc100k_max, inc100k_min)*1e5, 
                            color = sf)) +
  geom_point() +
  geom_hline(yintercept = c(inc100k_max*1e5, inc100k_min*1e5), linetype = 2, color = "grey")
## getting scaling factors 
scenario_scaled <- 
  foreach(i = 1:length(p_rabid_vals), .combine = rbind) %:%
  foreach(k = 1:nrow(scale_df_dist), .combine = rbind) %:%
  foreach(j = 1:length(rho_max_vals), .combine = rbind) %do% {
  check <- get.burden.fixed(names = dist_ttimes$mdg_dis_co, pop = dist_ttimes$pop, 
                     ttimes = dist_ttimes$ttimes/60, scenario = dist_ttimes$scenario,
                     B_ttimes = B_ttimes_dist, B_0 = B_0_dist, 
                     p_rabid = p_rabid_vals[i], 
                     rho_max = rho_max_vals[j], type = "burden", scale = TRUE, 
                     slope = scale_df_dist$sf[k], intercept = scale_df_dist$intercept[k])
  check$scale <- scale_df_dist$scale[k]
  check
  }

scenario_scaled %>%
  mutate(slope = case_when(slope == 0 & scale =="neg" ~ -10, 
                           slope == 0 & scale =="pos" ~ 10,
                           slope > 0 | slope < 0 ~ round(slope*1e10))) -> scenario_scaled_dist
scenario_scaled_dist %>%
  filter(scenario == 0) %>%
  group_by(slope, p_rabid, rho_max) %>%
  summarize(deaths = sum(deaths, na.rm = TRUE)) -> deaths_multivar

slope_name <- c(`-9` = "----", `-7` = "---", `-4` = "--", `-2` = "--",
                    `-10` =  "max", `9` = "++++", `7` = "+++", `4` = "++", `2` = "+",`10` =  "min")

ggplot(data = deaths_multivar, aes(x = p_rabid, y = deaths, color = rho_max)) +
  geom_point() +
  facet_grid(~ slope, labeller = labeller(slope = as_labeller(slope_name)))
ggplot(data = filter(scenario_scaled_dist, scenario == 0),  
       aes(x = ttimes, y = deaths/pop, color = p_rabid)) +
  geom_point() +
  facet_grid(rho_max ~ slope, labeller = labeller(slope = as_labeller(slope_name)))

scenario_scaled_dist %>%
  group_by(scenario, slope, p_rabid, rho_max) %>%
  summarize(deaths = sum(deaths)) -> deaths_scenario
deaths_scenario %>%
  left_join(select(deaths_multivar, slope, p_rabid, rho_max, deaths_base = deaths)) -> deaths_scenario
ggplot(data = deaths_scenario, aes(x = scenario, y = deaths/deaths_base, color = p_rabid)) +
  geom_point() +
  facet_grid(slope ~ rho_max, scales = "free_y")

@@

```{r commune scaling, cache = TRUE}
## Commune

## Commune ttimes
comm_ttimes <- read.csv("output/commune_temp_scenario_20190212_182810.csv", row.names = 1)
comm_ttimes <- as.data.table(comm_ttimes)
comm_ttimes$mdg_cm_ <- as.character(mada_communes$mdg_cm_)
comm_ttimes <- melt(comm_ttimes, id.vars = "mdg_cm_", value.name = "ttimes", variable.name = "scenario")
comm_ttimes$scenario <- as.numeric(gsub("result.", "", comm_ttimes$scenario))
comm_ttimes <- rbind(comm_ttimes, 
                       as.data.frame(list(mdg_cm_ = comm_catchments$mdg_cm_, scenario = 0,
                                          ttimes = comm_catchments$ttimes_weighted)))
comm_ttimes %>%
  left_join(select(comm_data, mdg_cm_, mdg_dis_co, pop)) -> comm_ttimes

@@

scale_df_comm <- rbind(as.data.frame(list(scale = "neg", 
                                     sf = seq(neg$coefficients[2], 0, length.out = 5),
                                     intercept = inc100k_max)),
                  as.data.frame(list(scale = "pos", 
                                     sf = seq(0, pos$coefficients[2], length.out = 5),
                                     intercept = inc100k_min)))
constrained_inc <- function(slope, intercept, pop, max, min){
  inc <- slope*pop + intercept
  inc[inc >= max] <- max
  inc[inc <= min] <- min
  return(inc)
}

scale_df_comm <- rbind(as.data.frame(list(scale = "neg", 
                                     sf = seq(neg$coefficients[2], 0, length.out = 5),
                                     intercept = inc100k_max)),
                  as.data.frame(list(scale = "pos", 
                                     sf = seq(0, pos$coefficients[2], length.out = 5),
                                     intercept = inc100k_min)))
constrained_inc <- function(slope, intercept, pop, max, min){
  inc <- slope*pop + intercept
  inc[inc >= max] <- max
  inc[inc <= min] <- min
  return(inc)
}
scale_df_comm %>%
  merge(., select(mada_communes@data, mdg_cm_, ttms_ll, pop = MDG__201)) -> scale_df_check_comm
ggplot(data = scale_df_check_comm, aes(x = log(pop), 
                            y = constrained_inc(sf, intercept, pop, inc100k_max, inc100k_min)*1e5, 
                            color = sf)) +
  geom_point() +
  geom_hline(yintercept = c(inc100k_max*1e5, inc100k_min*1e5), linetype = 2, color = "grey")

scenario_scaled <- 
  foreach(i = 1:length(p_rabid_vals), .combine = rbind) %:%
  foreach(k = 1:nrow(scale_df_comm), .combine = rbind) %:%
  foreach(j = 1:length(rho_max_vals), .combine = rbind) %do% {
  check <- get.burden.fixed(names = comm_ttimes$mdg_dis_co, pop = comm_ttimes$pop, 
                     ttimes = comm_ttimes$ttimes/60, scenario = comm_ttimes$scenario,
                     B_ttimes = B_ttimes_mada, B_0 = B_0_mada,
                     p_rabid = p_rabid_vals[i], 
                     rho_max = rho_max_vals[j], type = "burden", scale = TRUE, 
                     slope = scale_df_comm$sf[k], intercept = scale_df_comm$intercept[k])
  check %>% 
    group_by(names, scenario, p_rabid, rho_max, slope) %>%
    summarize(ttimes = mean(ttimes, na.rm = TRUE), pop = sum(pop, na.rm = TRUE),
              deaths = sum(deaths, na.rm = TRUE)) -> check
  check$scale <- scale_df_comm$scale[k]
  check
  }

scenario_scaled %>%
  mutate(slope = case_when(slope == 0 & scale =="neg" ~ -10, 
                           slope == 0 & scale =="pos" ~ 10,
                           slope > 0 | slope < 0 ~ round(slope*1e10))) -> scenario_scaled_comm

scenario_scaled_comm %>%
  filter(scenario == 0) %>%
  group_by(slope, p_rabid, rho_max) %>%
  summarize(deaths = sum(deaths, na.rm = TRUE)) -> deaths_multivar

slope_name <- c(`-9` = "----", `-7` = "---", `-4` = "--", `-2` = "--",
                    `-10` =  "max", `9` = "++++", `7` = "+++", `4` = "++", `2` = "+",`10` =  "min")

ggplot(data = deaths_multivar, aes(x = p_rabid, y = deaths, color = rho_max)) +
  geom_point() +
  facet_grid(~ slope, labeller = labeller(slope = as_labeller(slope_name)))
ggplot(data = filter(scenario_scaled_comm, scenario == 0),  
       aes(x = ttimes, y = deaths/pop, color = p_rabid)) +
  geom_point() +
  facet_grid(rho_max ~ slope, labeller = labeller(slope = as_labeller(slope_name)))

scenario_scaled_comm %>%
  group_by(scenario, slope, p_rabid, rho_max) %>%
  summarize(deaths = sum(deaths)) -> deaths_scenario
deaths_scenario %>%
  left_join(select(deaths_multivar, slope, p_rabid, rho_max, deaths_base = deaths)) -> deaths_scenario
ggplot(data = deaths_scenario, aes(x = scenario, y = deaths/deaths_base, color = p_rabid)) +
  geom_point() +
  facet_grid(slope ~ rho_max, scales = "free_y", labeller = labeller(slope = as_labeller(slope_name)))

>>>>

## Files
source("R/utils.R")
source("R/models.R")
source("R/data_functions.R")
source("R/get.burden.R")
select <- dplyr::select
knitr::opts_chunk$set(fig.pos = 'h', echo = FALSE, message = FALSE, warning = FALSE, 
                      include = TRUE)
```

@@

dist_ttimes <- cbind(dist_catchments$ttimes_weighted, dist_ttimes)
dist_mat <- matrix(NA, nrow(dist_ttimes), ncol(dist_ttimes))
dist_mat[, 1] <- dist_ttimes[, 1]
for (i in 2:ncol(dist_ttimes)){
  i = 3
  dist_mat[, i] <- ifelse(dist_ttimes[, i] < dist_ttimes[, i - 1], dist_ttimes[, i], NA)
}
dist_mat <- as.data.table(dist_mat)
dist_mat$mdg_dis_co <- as.character(mada_district$mdg_dis_co)
dist_mat <- melt(dist_mat, id.vars = "mdg_dis_co", value.name = "ttimes", variable.name = "scenario")
dist_mat$scenario <- as.numeric(gsub("V", "", dist_mat$scenario)) - 1

@@

results_comm_med <- get.burden.stochastic(names = comm_mat$mdg_cm_, ttimes = comm_mat$ttimes/60,
                           pop = comm_mat$pop, scenario = comm_mat$scenario,
                           param_ttimes = B_ttimes_mada,
                           param_intercept = B_0_mada,
                           p_rab_min = 0.2, p_rab_max = 0.6, rho_max = 0.98,
                           max_HDR = 25, min_HDR = 5, 
                           dog_rabies_inc = 0.01, human_exp_rate = 0.39, 
                           prob_death = 0.16, nsims = 2)

@@

results_dist_med <- get.burden.stochastic(names = dist_mat$mdg_dis_co, ttimes = dist_mat$ttimes/60,
                           pop = dist_mat$pop, scenario = dist_mat$scenario,
                           param_ttimes = B_ttimes_dist,
                           param_intercept = B_0_dist,
                           p_rab_min = 0.2, p_rab_max = 0.6, rho_max = 0.98,
                           max_HDR = 25, min_HDR = 5, 
                           dog_rabies_inc = 0.01, human_exp_rate = 0.39, 
                           prob_death = 0.16, nsims = 2)

@@

``` {r scenario, cache = TRUE}
## Plotting national level
ggplot(data = results_natl, aes (x = scenario, y = deaths_mean, color = model)) +
  geom_line() +
  geom_ribbon(aes(ymin = deaths_upperCI, ymax = deaths_lowerCI, 
                  color = NULL, fill = model),
              alpha = 0.5) +
  scale_color_manual(values = c("district" = "blue", 
                                "commune" = "purple"), 
                     guide = "none") +
  scale_fill_manual(values = c("district" = "blue", 
                                "commune" = "purple")) +
  guides(color = guide_legend(), 
         fill = guide_legend(override.aes = list(linetype = 1))) +
  xlab("# of Additional ARMC") +
  ylab("Mean annual deaths \n due to rabies") +
  labs(tag = "A") -> e

@@

@@

We use this to estimate how vaccine demand will change as access to PEP is expanded...
```{r simulate vials used}
## Get catchment
catch_scenario <- read.csv("output/temp_ARMC.csv", row.names = 1)
comm_ttimes <- read.csv("output/commune_temp_scenario_20190212_182810.csv", row.names = 1)[, 1:231]
mada_communes@data %>%
  left_join(comm_data) -> comm_catches
comm_ttimes <- cbind(comm_ttimes[, 1], comm_ttimes)
names(comm_ttimes)[1] <- "result.0"
comm_mat <- matrix(NA, nrow(comm_ttimes), ncol(comm_ttimes))
comm_mat[, 1] <- as.character(comm_catches$CTAR)

for (i in 2:ncol(comm_ttimes)){
  comm_mat[, i] <- ifelse(comm_ttimes[, i] < comm_ttimes[, i - 1], as.character(catch_scenario$CTAR[i - 1]), 
                          comm_mat[, 1])
}

comm_mat <- as.data.table(comm_mat)
comm_mat$mdg_cm_ <- mada_communes$mdg_cm_
comm_mat <- melt(comm_mat, id.vars = "mdg_cm_", value.name = "catchment", variable.name = "scenario")
comm_mat$scenario <- as.numeric(gsub("V", "", comm_mat$scenario)) - 1
comm_ttimes <- as.data.table(comm_ttimes)
comm_ttimes$mdg_cm_ <- mada_communes$mdg_cm_
comm_ttimes <- melt(comm_ttimes, id.vars = "mdg_cm_", value.name = "ttimes", variable.name = "scenario")
comm_ttimes$scenario <- as.numeric(gsub("result.", "", comm_ttimes$scenario))

comm_mat %>%
  left_join(comm_ttimes) %>%
  left_join(select(mada_communes@data, pop = MDG__201, mdg_cm_)) %>%
  mutate(exp_bites = inv.logit(B_ttimes_mada*ttimes/60 + B_0_mada)*pop) %>%
  group_by(scenario, catchment) %>%
  summarize(bites = sum(exp_bites, na.rm = TRUE)) %>%
  drop_na(catchment) -> comm_master

sim.throughput <- function(bites, nsims = 100) {
  get.vials <- function(x) {
    day0 <- round(runif(rpois(1, x), min = 1, max = 365))
    days <- c(day0, day0 + 3, day0 + 7)
    vials <- sum(ceiling(table(days)/2))
    return(vials)
  }

  check <- foreach(i = 1:nsims, .combine = cbind) %dopar% {
    vials <- sapply(bites, get.vials, simplify = TRUE)
  }

  mean_vials <- rowMeans(check, na.rm = TRUE)
  sd_vials <- apply(check, 1, sd, na.rm = TRUE)
  return(as.data.frame(list(bites = bites, mean_vials = mean_vials, sd_vials = sd_vials)))
}

## local cluster
library(doParallel)
# Calculate the number of cores
no_cores <- detectCores() - 1
# Initiate cluster
cl <- makeCluster(no_cores)
registerDoParallel(cl)
system.time({throughput <- sim.throughput(bites = comm_master$bites, nsims = 10)})
stopCluster(cl) ## for doParallel

comm_throughput <- bind_cols(comm_master, throughput)

```{r throughput district}
## Get catchment
catch_scenario <- read.csv("output/temp_ARMC.csv", row.names = 1)
dist_ttimes <- read.csv("output/district_temp_scenario_20190212_181056.csv", row.names = 1)
dist_ttimes <- cbind(dist_ttimes[, 1], dist_ttimes)
names(dist_ttimes)[1] <- "result.0"
dist_mat <- matrix(NA, nrow(dist_ttimes), ncol(dist_ttimes))
dist_mat[, 1] <- as.character(mada_district$CTAR)

for (i in 2:ncol(dist_ttimes)){
  dist_mat[, i] <- ifelse(dist_ttimes[, i] < dist_ttimes[, i - 1], as.character(catch_scenario$CTAR[i - 1]), 
                          dist_mat[, 1])
}

dist_mat <- as.data.table(dist_mat)
dist_mat$mdg_dis_co <- mada_district$mdg_dis_co
dist_mat <- melt(dist_mat, id.vars = "mdg_dis_co", value.name = "catchment", variable.name = "scenario")
dist_mat$scenario <- as.numeric(gsub("V", "", dist_mat$scenario)) - 1
dist_ttimes <- as.data.table(dist_ttimes)
dist_ttimes$mdg_dis_co <- mada_district$mdg_dis_co
dist_ttimes <- melt(dist_ttimes, id.vars = "mdg_dis_co", value.name = "ttimes", variable.name = "scenario")
dist_ttimes$scenario <- as.numeric(gsub("result.", "", dist_ttimes$scenario))

dist_mat %>%
  left_join(dist_ttimes) %>%
  left_join(select(mada_district@data, pop = pop2015adj, mdg_dis_co)) %>%
  mutate(exp_bites = inv.logit(B_ttimes_dist*ttimes/60 + B_0_dist)*pop) %>%
  group_by(scenario, catchment) %>%
  summarize(bites = sum(exp_bites, na.rm = TRUE)) %>%
  drop_na(catchment) -> dist_master

## local cluster
library(doParallel)
# Calculate the number of cores
no_cores <- detectCores() - 1
# Initiate cluster
cl <- makeCluster(no_cores)
registerDoParallel(cl)
system.time({throughput <- sim.throughput(bites = dist_master$bites, nsims = 10)})
stopCluster(cl) ## for doParallel

dist_throughput <- bind_cols(dist_master, throughput)

@@

### S5. Sensitity analyses for burden estimates
#### District
```{r scaling w/ pop, cache = TRUE}
## Dist ttimes
dist_ttimes <- read.csv("output/district_temp_scenario_20190212_181056.csv", row.names = 1)
dist_ttimes <- as.data.table(dist_ttimes)
dist_ttimes$mdg_dis_co <- as.character(mada_district$mdg_dis_co)
dist_ttimes <- melt(dist_ttimes, id.vars = "mdg_dis_co", value.name = "ttimes", variable.name = "scenario")
dist_ttimes$scenario <- as.numeric(gsub("result.", "", dist_ttimes$scenario))
dist_ttimes <- rbind(dist_ttimes, 
                       as.data.frame(list(mdg_dis_co = dist_catchments$mdg_dis_co, scenario = 0,
                                          ttimes = dist_catchments$ttimes_weighted)))
dist_ttimes %>%
  left_join(select(mada_district@data, mdg_dis_co, district, pop = pop2015adj)) -> dist_ttimes

@@

scale_df_dist %>%
  merge(., select(mada_district@data, mdg_dis_co, ttimes_weighted, pop = pop2015adj)) -> scale_df_check_dist

A_dist <- ggplot(data = scale_df_check_dist, aes(x = log(pop), 
                            y = constrained_inc(sf, intercept, pop, inc100k_max, inc100k_min)*1e5, 
                            color = sf)) +
  geom_point() +
  geom_hline(yintercept = c(inc100k_max*1e5, inc100k_min*1e5), linetype = 2, color = "grey") +
  scale_color_gradient2(low = "red", mid = "grey50", high = "blue", midpoint = 0, name = "Scaling Factor") +
  ylab("Rabies exposures per \n 100k persons") +
  xlab("Human population size (log)")

system.time({
scenario_natl_dist <- 
  foreach(i = 1:length(p_rabid_vals), .combine = rbind) %:%
  foreach(k = 1:nrow(scale_df_dist), .combine = rbind) %:%
  foreach(j = 1:length(rho_max_vals), .combine = rbind) %do% {
  check <- get.burden.fixed(names = dist_ttimes$mdg_dis_co, pop = dist_ttimes$pop, 
                     ttimes = dist_ttimes$ttimes/60, scenario = dist_ttimes$scenario,
                     B_ttimes = B_ttimes_mada, B_0 = B_0_mada,
                     p_rabid = p_rabid_vals[i], 
                     rho_max = rho_max_vals[j], type = "burden", scale = TRUE, 
                     slope = scale_df_dist$sf[k], intercept = scale_df_dist$intercept[k])
  check$scale <- scale_df_dist$scale[k]
  check %>% 
    group_by(p_rabid, rho_max, slope, scale, scenario) %>% 
    summarize(deaths = sum(deaths, na.rm = TRUE)) -> check
  check
  }
})

dist_base <- filter(dist_ttimes, scenario == 0)

system.time({
scenario_base_dist <- 
  foreach(i = 1:length(p_rabid_vals), .combine = rbind) %:%
  foreach(k = 1:nrow(scale_df_dist), .combine = rbind) %:%
  foreach(j = 1:length(rho_max_vals), .combine = rbind) %do% {
  check <- get.burden.fixed(names = dist_base$mdg_dis_co, pop = dist_base$pop, 
                     ttimes = dist_base$ttimes/60, scenario = dist_base$scenario,
                     B_ttimes = B_ttimes_mada, B_0 = B_0_mada,
                     p_rabid = p_rabid_vals[i], 
                     rho_max = rho_max_vals[j], type = "burden", scale = TRUE, 
                     slope = scale_df_dist$sf[k], intercept = scale_df_dist$intercept[k])
  check$scale <- scale_df_dist$scale[k]
  check
  }
})

scenario_natl_dist %>%
  mutate(slope_order = case_when(slope == 0 & scale =="neg" ~ -10, 
                           slope == 0 & scale =="pos" ~ 10,
                           slope > 0 | slope < 0 ~ round(slope*1e10)), 
         slope_order = round(1/slope_order, 2), 
         slope_order = ifelse(slope_order == -0.1, -Inf, 
                                 ifelse(slope_order == 0.1, Inf, slope_order))) -> scenario_scaled_dist
scenario_base_dist %>%
   mutate(slope_order = case_when(slope == 0 & scale =="neg" ~ -10, 
                           slope == 0 & scale =="pos" ~ 10,
                           slope > 0 | slope < 0 ~ round(slope*1e10)), 
         slope_order = round(1/slope_order, 2), 
         slope_order = ifelse(slope_order == -0.1, -Inf, 
                                 ifelse(slope_order == 0.1, Inf, slope_order))) -> scenario_base_dist
scenario_base_dist %>%
  group_by(slope_order, p_rabid, rho_max) %>%
  summarize(deaths = sum(deaths, na.rm = TRUE)) -> deaths_multivar

slope_name_dist <- c(`-0.11` = "----", `-0.14` = "---", `-0.25` = "--", `-0.5` = "-",
                `-Inf` =  "max", `0.11` = "++++", `0.14` = "+++", `0.25` = "++", 
                `0.5` = "+",`Inf` =  "min")

B_dist <- ggplot(data = deaths_multivar, aes(x = p_rabid, y = deaths, color = rho_max)) +
  geom_point() +
  facet_grid(~ slope_order, labeller = labeller(slope_order = as_labeller(slope_name_dist))) +
  xlab("Prop. of reported \n bites assumed \n to be rabid") +
  ylab("Burden of rabies deaths \n at national level") +
  scale_x_continuous(breaks = c(0.2, 0.6)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_gradient(name = "Maximum \n reporting")

C_dist <- ggplot(data = scenario_base_dist,  
       aes(x = ttimes, y = deaths/pop*1e5, color = p_rabid)) +
  geom_point() +
  facet_grid(rho_max ~ slope_order, labeller = labeller(slope_order = as_labeller(slope_name_dist))) +
  scale_color_gradient(name = "Proportion of reported \n bites assumed \n to be rabid") + 
  ylab("Rabies deaths \n per 100k persons") +
  xlab("Travel times (hours)") +
  scale_x_continuous(breaks = c(0, 6, 12)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

scenario_scaled_dist %>%
  filter(scenario == 0) %>%
  mutate(deaths_base = deaths) %>%
  select(-deaths, -scenario) %>%
  right_join(scenario_scaled_dist) -> deaths_scenario_dist

D_dist <- ggplot(data = deaths_scenario_dist, aes(x = scenario, y = deaths/deaths_base, color = p_rabid)) +
  geom_point() +
  facet_grid(rho_max ~ slope_order, 
             labeller = labeller(slope_order = as_labeller(slope_name_dist))) +
  scale_color_gradient(name = "Proportion of reported \n bites assumed \n to be rabid") + 
  scale_x_continuous(breaks = c(0, 250, 500)) +
  scale_y_continuous(breaks = c(0, 0.5, 1), limits = c(0, 1)) + 
  xlab("# Additional ARMC") +
  ylab("Proportion of baseline burden") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

```{r commune scaling, cache = TRUE}
## Commune
## Commune ttimes
comm_ttimes <- read.csv("output/commune_temp_scenario_20190212_182810.csv", row.names = 1)
comm_ttimes <- as.data.table(comm_ttimes)
comm_ttimes$mdg_cm_ <- as.character(mada_communes$mdg_cm_)
comm_ttimes <- melt(comm_ttimes, id.vars = "mdg_cm_", value.name = "ttimes", variable.name = "scenario")
comm_ttimes$scenario <- as.numeric(gsub("result.", "", comm_ttimes$scenario))
comm_ttimes <- rbind(comm_ttimes, 
                       as.data.frame(list(mdg_cm_ = comm_catchments$mdg_cm_, scenario = 0,
                                          ttimes = comm_catchments$ttimes_weighted)))
comm_ttimes %>%
  left_join(select(comm_data, mdg_cm_, mdg_dis_co, pop)) -> comm_ttimes

@@

scale_df_comm <- rbind(as.data.frame(list(scale = "neg", 
                                     sf = seq(neg$coefficients[2], 0, length.out = 5),
                                     intercept = inc100k_max)),
                  as.data.frame(list(scale = "pos", 
                                     sf = seq(0, pos$coefficients[2], length.out = 5),
                                     intercept = inc100k_min)))

constrained_inc <- function(slope, intercept, pop, max, min){
  inc <- slope*pop + intercept
  inc[inc >= max] <- max
  inc[inc <= min] <- min
  return(inc)
}

scale_df_comm %>%
  merge(., select(mada_communes@data, mdg_cm_, ttms_ll, pop = MDG__201)) -> scale_df_check_comm

scale_df_check_comm$admin <- "commune"
scale_df_check_dist$admin <- "district"
scale_df_check <- bind_rows(scale_df_check_dist, scale_df_check_comm)

A_comm <- ggplot(data = scale_df_check_comm, aes(x = log(pop), 
                            y = constrained_inc(sf, intercept, pop, inc100k_max, inc100k_min)*1e5, 
                            color = sf)) +
  geom_point() +
  geom_hline(yintercept = c(inc100k_max*1e5, inc100k_min*1e5), linetype = 2, color = "grey") +
  scale_color_gradient2(low = "red", mid = "grey50", high = "blue", midpoint = 0, name = "Scaling Factor", 
                        guide = "none") +
  ylab("Rabies exposures per \n 100k persons") +
  xlab("Human population size (log)")

system.time({
scenario_natl_comm <- 
  foreach(i = 1:length(p_rabid_vals), .combine = rbind) %:%
  foreach(k = 1:nrow(scale_df_comm), .combine = rbind) %:%
  foreach(j = 1:length(rho_max_vals), .combine = rbind) %do% {
  check <- get.burden.fixed(names = comm_ttimes$mdg_cm_, pop = comm_ttimes$pop, 
                     ttimes = comm_ttimes$ttimes/60, scenario = comm_ttimes$scenario,
                     B_ttimes = B_ttimes_mada, B_0 = B_0_mada,
                     p_rabid = p_rabid_vals[i], 
                     rho_max = rho_max_vals[j], type = "burden", scale = TRUE, 
                     slope = scale_df_comm$sf[k], intercept = scale_df_comm$intercept[k])
  check$scale <- scale_df_comm$scale[k]
  check %>% 
    group_by(p_rabid, rho_max, slope, scale, scenario) %>% 
    summarize(deaths = sum(deaths, na.rm = TRUE)) -> check
  check
  }
})

comm_base <- filter(comm_ttimes, scenario == 0)

system.time({
scenario_base_comm <- 
  foreach(i = 1:length(p_rabid_vals), .combine = rbind) %:%
  foreach(k = 1:nrow(scale_df_comm), .combine = rbind) %:%
  foreach(j = 1:length(rho_max_vals), .combine = rbind) %do% {
  check <- get.burden.fixed(names = comm_base$mdg_cm_, pop = comm_base$pop, 
                     ttimes = comm_base$ttimes/60, scenario = comm_base$scenario,
                     B_ttimes = B_ttimes_mada, B_0 = B_0_mada,
                     p_rabid = p_rabid_vals[i], 
                     rho_max = rho_max_vals[j], type = "burden", scale = TRUE, 
                     slope = scale_df_comm$sf[k], intercept = scale_df_comm$intercept[k])
  check$scale <- scale_df_comm$scale[k]
  check
  }
})

scenario_natl_comm %>%
  mutate(slope_order = case_when(slope == 0 & scale =="neg" ~ -10, 
                           slope == 0 & scale =="pos" ~ 10,
                           slope > 0 | slope < 0 ~ round(slope*1e9, 2)), 
         slope_order = round(1/slope_order, 2), 
         slope_order = ifelse(slope_order == -0.1, -Inf, 
                                 ifelse(slope_order == 0.1, Inf, slope_order))) -> scenario_scaled_comm
scenario_base_comm %>%
   mutate(slope_order = case_when(slope == 0 & scale =="neg" ~ -10, 
                           slope == 0 & scale =="pos" ~ 10,
                           slope > 0 | slope < 0 ~ round(slope*1e9, 2)), 
         slope_order = round(1/slope_order, 2), 
         slope_order = ifelse(slope_order == -0.1, -Inf, 
                                 ifelse(slope_order == 0.1, Inf, slope_order))) -> scenario_base_comm
scenario_base_comm %>%
  group_by(slope_order, p_rabid, rho_max) %>%
  summarize(deaths = sum(deaths, na.rm = TRUE)) -> deaths_multivar

slope_name_comm <- c(`-0.19` = "----", `-0.25` = "---", `-0.37` = "--", `-0.75` = "-",
                `-Inf` =  "max", `0.19` = "++++", `0.25` = "+++", `0.37` = "++", 
                `0.75` = "+",`Inf` =  "min")

B_comm <- ggplot(data = deaths_multivar, aes(x = p_rabid, y = deaths, color = rho_max)) +
  geom_point() +
  facet_grid(~ slope_order, labeller = labeller(slope_order = as_labeller(slope_name_comm))) +
  xlab("Prop. of reported \n bites assumed \n to be rabid") +
  ylab("Burden of rabies deaths \n at national level") +
  scale_x_continuous(breaks = c(0.2, 0.6)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_gradient(name = "Maximum \n reporting", guide = "none")

C_comm <- ggplot(data = scenario_base_comm,  
       aes(x = ttimes, y = deaths/pop*1e5, color = p_rabid)) +
  geom_point() +
  facet_grid(rho_max ~ slope_order, labeller = labeller(slope_order = as_labeller(slope_name_comm))) +
  scale_color_gradient(name = "Proportion of reported \n bites assumed \n to be rabid", guide = "none") + 
  ylab("Rabies deaths \n per 100k persons") +
  xlab("Travel times (hours)") +
  scale_x_continuous(breaks = c(0, 6, 12)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

scenario_scaled_comm %>%
  filter(scenario == 0) %>%
  mutate(deaths_base = deaths) %>%
  select(-deaths, -scenario) %>%
  right_join(scenario_scaled_comm) -> deaths_scenario_comm
